---
title: "Untitled"
format: html
editor: visual
---

```{r}
library(tidyverse)
library(sf)
library(terra)
library(tmap)
library(tmaptools)
```

```{r}
# Set directory for folder
pre_fire_dir <- here::here("data", "LC80340322016189-SC20170128091153")

# Create a list of all images that have the extension .tif and contain the word band
pre_fire_bands <- list.files(pre_fire_dir,
                             pattern = glob2rx("*band*.tif$"),
                             full.names = TRUE)
# Create a raster stack
pre_fire_rast <- rast(pre_fire_bands)

# Read mask raster
pre_mask <- rast(here::here("data", "LC80340322016189-SC20170128091153", "LC80340322016189LGN00_cfmask_crop.tif"))
```

```{r}
# Set directory for folder
post_fire_dir <- here::here("data", "LC80340322016205-SC20170127160728")

# Create a list of all images that have the extension .tif and contain the word band
post_fire_bands <- list.files(post_fire_dir,
                             pattern = glob2rx("*band*.tif$"),
                             full.names = TRUE)
# Create a raster stack
post_fire_rast <- rast(post_fire_bands)

# Read mask raster
post_mask <- rast(here::here("data", "LC80340322016189-SC20170128091153", "LC80340322016189LGN00_cfmask_crop.tif"))
```

```{r}
nbr_fun <- function(nir, swir2){
    (nir - swir2)/(nir + swir2)
}
```

# 3. Your task
Rename the bands of the pre_fire and post_fire rasters using names()
```{r}
bands <- c("Aerosol", "Blue", "Green", "Red", "NIR", "SWIR1", "SWIR2")

names(pre_fire_rast) <- bands
names(post_fire_rast) <- bands
```

Next, for each of the pre_fire and post_fire rasters…
Mask out clouds and shadows with the pre_mask and post_mask rasters
Hint: Set mask > 0 to NA
```{r}
pre_mask[pre_mask > 0] <- NA
post_mask[post_mask > 0] <- NA

pre_fire_rast <- mask(pre_fire_rast, mask = pre_mask)
post_fire_rast <- mask(post_fire_rast, mask = post_mask)

```

Plot a true color composite using plotRGB()
Map the red band to the red channel, green to green, and blue to blue
Apply a linear stretch “lin” or histogram equalization “hist”
```{r}
plot(pre_fire_rast, colNA = "white")
plot(post_fire_rast, colNA = "white")

```

True color
```{r}
plotRGB(pre_fire_rast, r = 4, g = 3, b = 2, stretch = "lin", colNA = "black")
```
```{r}
plotRGB(post_fire_rast, r = 4, g = 3, b = 2, stretch = "lin", colNA = "black")
```
False color
Plot two false color composite using plotRGB()
Map the SWIR2 band to the red channel, NIR to green, and green to blue
Apply a linear stretch “lin” or histogram equalization “hist”
```{r}
plotRGB(pre_fire_rast, r = 7, g = 5, b = 3, stretch = "lin", colNA = "black")
plotRGB(post_fire_rast, r = 7, g = 5, b = 3, stretch = "lin", colNA = "black")
```

Calculate the normalized burn ratio (NBR)
Hint: Use lapp() like you previously did for NDVI and NDWI in Week 4
```{r}
pre_nbr <- terra::lapp(pre_fire_rast[[c(5, 7)]], 
            fun = nbr_fun)

post_nbr <- terra::lapp(post_fire_rast[[c(5, 7)]], 
            fun = nbr_fun)

diff_nbr = pre_nbr - post_nbr
plot(diff_nbr)
```

Find the difference NBR, where 
```{r}
diff <- pre_fire_rast - post_fire_rast

```

